Automatic Identification and Annotation of Tasks in Structured Programs

### 2018-04-09 docs/ACM/paper.tex
Adding new figures.

\noindent
\textbf{Benchmarking:}
we have used different benchmarks in our experiments.
In Sections~\ref{sub:performance} and~\ref{sub:optimizations} we use
\textsf{BSC-Bots}\footnote{\url{https://github.com/bsc-pm/bots/tree/master/serial}} and \textsf{Swan}\footnote{\url{http://cuda.dcc.ufmg.br/swan/}}~\cite{Moreira17}.
In Section~\ref{sub:versatility} we use the LLVM test suite, and in
Section~\ref{sub:scalability} we use random programs produced with
\textsf{CSmith}~\cite{Yang11}.
Runtime numbers are averages of five executions.
We have not changed manually any of the benchmarks.

@@

\begin{figure}[h]
\begin{center}
\includegraphics[width=1.1\columnwidth]{images/EVAL1_bots_and_toys.png}
\caption{Speedup comparisons -- automatic annotations compare favourably against
manual interventions, and lead to great performance gains.
The Y-axis shows the speedup of either manual intervention, or automatic
annotation (this paper) onto the original programs.}
\label{fig:Absolute_speedups}
\end{center}
\end{figure}

@@

\begin{figure}[htb]
\begin{center}
\includegraphics[width=1\columnwidth]{images/EVAL2_opt.png}
\caption{The benefit of our optimizations.
Each optimization (cost model and recursion bounds) lead to
non-trivial speedups.}
\label{fig:Opt_Speedups}
\end{center}
\end{figure}

@@

\begin{figure}[htb]
\begin{center}
\includegraphics[width=1\columnwidth]{images/EVAL3_test-suite.png}
\caption{{\Taskminer}'s performance in the real world. This chart shows that our algorithm also performs
well on programs that are not deemed inherently parallel, being able to find hidden parallelism
in 20 programs from LLVM's Test Suite.}
\label{fig:testsuite}
\end{center}
\end{figure}

>>>>

\noindent
\textbf{Benchmarking:}
we have used different benchmarks in our experiments.
In Sections~\ref{sub:performance} and~\ref{sub:optimizations} we use
\textsf{BSC-Bots}\footnote{\url{https://github.com/bsc-pm/bots/tree/master/serial}}~\cite{Duran09} and
\textsf{Swan}\footnote{\url{http://cuda.dcc.ufmg.br/swan/}}~\cite{Moreira17}.
In Section~\ref{sub:versatility} we use the LLVM test suite, and in
Section~\ref{sub:scalability} we use random programs produced with
\textsf{CSmith}~\cite{Yang11}.
Runtime numbers are averages of five executions.
We have not changed manually any of the benchmarks.

@@

\begin{figure}[h]
\begin{center}
\includegraphics[width=1\columnwidth]{images/TM_Performance}
\caption{Speedup comparisons -- automatic annotations compare favourably against
manual interventions, and lead to great performance gains.
The Y-axis shows the speedup of either manual intervention, or automatic
annotation (this paper) onto the original programs.}
\label{fig:TM_Performance}
\end{center}
\end{figure}

@@

\begin{figure}[htb]
\begin{center}
\includegraphics[width=1\columnwidth]{images/Stub}
\caption{The benefit of our optimizations.
Each optimization (cost model and recursion bounds) lead to
non-trivial speedups.}
\label{fig:Opt_Speedups}
\end{center}
\end{figure}

@@

\begin{figure}[htb]
\begin{center}
\includegraphics[width=1\columnwidth]{images/Stub}
\caption{{\Taskminer}'s performance in the real world. This chart shows that our algorithm also performs
well on programs that are not deemed inherently parallel, being able to find hidden parallelism
in 20 programs from LLVM's Test Suite.}
\label{fig:testsuite}
\end{center}
\end{figure}
